\Title

### 2021-06-02 manuscript/content.tex
Extend Australia section (#154)
Redo cross-validation using K-Fold and RMS as score. Generate more plots for
the manuscript: window size vs memory needed, RMS scores of cross-validation,
RMS vs iterations, map of the residuals with histogram inset. Add a few more
latex variables for the manuscript.

Secondly, we need to determine the depth of the sources and the value for the
damping parameter. Based on the results obtained in
Section~\ref{sec:synthetic_distributions}, we have chosen to locate them using
the \emph{relative depth} strategy.
In order to determine the values for the \emph{depth} and \emph{damping}
parameters, we have applied a K-Fold cross-validation method through the
scikit-learn implementation \citep{sklearn2011}.
It consists in randomly dividing the original data into $k$ small sets (or
folds), estimate the source coefficients using only $k - 1$ of the folds
(training data) and validate the model by comparing its predictions with the
remaining fold (testing data). This process is carried out once for each one of
the $k$ folds.
With the goal of speeding up the computations, we selected a portion of the
Australia gravity disturbances to run the cross-validation: an area of
\AustraliaSmallAreaEastingSize{}$\times$\AustraliaSmallAreaNorthingSize{}
containing \AustraliaSmallAreaNPoints points.
We run the cross-validation with a combination of \emph{depth} ranging from
\AustraliaDepthMin{} to \AustraliaDepthMax{},
and \emph{damping} from
\AustraliaDampingMin{} to \AustraliaDampingMax{} in steps of one order of
magnitude.
We have used the root-mean square error as the validation function between the
testing data and the predictions on each k-fold and computed the mean of all
the RMS for each combination of the \emph{depth} and \emph{damping} parameters.
Figure \ref{fig:australia-memory-cv-error}b shows the resulting scores of the
cross-validation and highlights the minimum value achieved:
\AustraliaEqlRmsScore{} corresponding to a relative depth of \AustraliaEqlDepth{} and
a damping equal to \AustraliaEqlDamping{}.

Finally, we proceed to estimate the coefficients of the whole set of
gradient-boosted equivalent sources using the parameters previously determined.
Fig.~\ref{fig:australia-memory-cv-error}c shows the root-mean square of the
residuals after each iteration of the gradient-boosting algorithm, exposing how
to algorithm converges at a minimum difference between the gravity disturbance
data and the predicted values by the equivalent sources.
We then used the estimated source coefficients to predict the values of the
gravity disturbance on a regular grid of
\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
\AustraliaEqlGridHeight{} above the ellipsoid.
Fig.~\ref{fig:australia} shows the original data distribution and the
interpolated regular grid.
Grid points that are further than 50\km{} from the nearest data
point are masked to avoid unrealistic extrapolations.

>>>>

Secondly, we need to determine the depth of the sources and the value for the
damping parameter. Based on the results obtained in
Section~\ref{sec:synthetic_distributions}, we have chosen to locate them using
the \emph{relative depth} strategy.
In order to determine the values for the \emph{depth} and \emph{damping}
parameters, we have applied a K-Fold cross-validation method through the
scikit-learn implementation \citep{sklearn2011}.
It consists in randomly dividing the original data into $k$ small sets (or
folds), estimate the source coefficients using only $k - 1$ of the folds
(training data) and validate the model by comparing its predictions with the
remaining fold (testing data). This process is carried out once for each one of
the $k$ folds.
With the goal of speeding up the computations, we selected a portion of the
Australia gravity disturbances to run the cross-validation: an area of
\AustraliaSmallAreaEastingSize{}$\times$\AustraliaSmallAreaNorthingSize{}
containing \AustraliaSmallAreaNPoints{} points.
We run the cross-validation with a combination of \emph{depth} ranging from
\AustraliaDepthMin{} to \AustraliaDepthMax{},
and \emph{damping} from
\AustraliaDampingMin{} to \AustraliaDampingMax{} in steps of one order of
magnitude.
We have used the root-mean square error as the validation function between the
testing data and the predictions on each k-fold and computed the mean of all
the RMS for each combination of the \emph{depth} and \emph{damping} parameters.
Figure \ref{fig:australia-memory-cv-error}b shows the resulting scores of the
cross-validation and highlights the minimum value achieved:
\AustraliaEqlRmsScore{} corresponding to a relative depth of \AustraliaEqlDepth{} and
a damping equal to \AustraliaEqlDamping{}.

Finally, we proceed to estimate the coefficients of the whole set of
gradient-boosted equivalent sources using the parameters previously determined.
Fig.~\ref{fig:australia-memory-cv-error}c shows the root-mean square of the
residuals after each iteration of the gradient-boosting algorithm, exposing how
the algorithm converges at a minimum difference between the gravity disturbance
data and the predicted values by the equivalent sources.
We then used the estimated source coefficients to predict the values of the
gravity disturbance on a regular grid of
\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
\AustraliaEqlGridHeight{} above the ellipsoid.
Fig.~\ref{fig:australia} shows the original data distribution and the
interpolated regular grid.
Grid points that are further than 50\km{} from the nearest data
point are masked to avoid unrealistic extrapolations.
